Total Team Spending and Profitability Results in a Higher League Ranking in the English Premier League

### 2024-04-22 paper/paper.qmd
Committing all work done up to 04-21-2024 at 9:57pm.

## Analyzing Chelsea F.C.'s Underachievement: An Outlier Case Study

Within the predictions lies a couple outliers, with Chelsea F.C. being the most notable. Chelsea's actual points stand at 47, while the model predicted they would have achieved 58 points by Matchday 33. This discrepancy of 11 points is significant and suggests that Chelsea F.C. is underperforming relative to its financial status. As a club known to have a substantial payroll and high market value, which are indicators of a team's wealth and resources available for acquiring talent, the expectation would be for Chelsea to secure a position closer to the top of the table.

@@

## Second discussion point

## Third discussion point

>>>>

## Analyzing Chelsea F.C.'s Underachievement

Within the predictions lies a couple outliers, with Chelsea F.C. being the most notable. Chelsea's actual points stand at 47, while the model predicted they would have achieved 58 points by Matchday 33. This discrepancy of 11 points is significant and suggests that Chelsea F.C. is underperforming relative to its financial status. As a club known to have a substantial payroll and high market value, and a significant fan base, which are indicators of a team's wealth and resources available for acquiring talent, the expectation would be for Chelsea to secure a position closer to the top of the table.

@@

## Analyzing Fulham F.C.'s Overachievement

Despite having relatively modest financial metrics compared to the league's top spenders, Fulham F.C. managed to outperform the projections. Fulham's actual points stand at 42 (12th place), while the model predicted they would have achieved only 31 points (17th place) by Matchday 33. This suggests that Fulham F.C. is outperforming relative to their financial status.

This suggests that their are ways in which other areas of the game besides financial metrics lead to higher league rankings. This could include effective management, coaching, and perhaps strong team cohesion that transcends financial capabilities. Perhaps Fulham's management has excelled this season in areas such as player development, game strategy, and optimizing team dynamics. Management strategies and the coaching staff's ability to maximize player potential and tactical execution on a budget far less then their more successful counterparts could aid other clubs in understanding how to maximize results while minimizing expenditures.
